On the formation of H$\alpha$ line emission around classical T Tauri stars: the disc-wind-magnetosphere hybrid model

### 2006-01-30 TTau_Halpha/kurosawa.tex
Typo corrections done. The reference are now inserted in the main text!!! (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@648 25464f21-6099-402c-b30a-640f1d40d38b

\usepackage{babel}
\makeatother
\begin{document}
\title[On the formation of H$\alpha$ around classical T Tauri
  stars]{On the formation of H$\alpha$ line emission around classical
  T Tauri star: the disc-wind-magnetosphere hybrid model}

@@

  \caption{Basic model configuration of the disc-wind-magnetosphere
    hybrid model. The system consist of four components: (1)~the
    continuum source located at the origin $\left( o \right)$ of the
    cartesian coordinates $\left(x,y,z\right)$ -- the $y$-axis is into
    the paper, (2)~the magnetospheric accretion flow, (3)~the disc
    wind, and (4)~the accretion disc. The disc wind originates from
    the disc surface between $w_{i}=R_{\mathrm{wi}}$ and
    $w_{i}=R_{\mathrm{wo}}$ where $w_{i}$ is the distance from the $z$
    axis on the equatorial plane.  The wind source
    points ($S$), from which the stream lines diverges, are placed at
    distance $d$ above and below the star. The degree of wind
    collimation is controlled by changing the value of $d$.}

@@

\citet*{knigge:1995} introduced the {}``split-monopole'' kinematic
disc-wind model in their studies of the UV resonance lines formed
in the winds of cataclysmic variable stars. His formalism provides
a simple parameterisation of a disc wind that has similar properties 
to those found by  MHD modelling. In this model, the outflow
arises from the surface of the rotating accretion disc, and has a
biconical geometry. The specific angular momentum is assumed to be
conserved along a stream line, and the poloidal velocity component
is assumed to be simply a radial from vertically displaced {}``sources''
from the central star.  Here we briefly describe the disc-wind model, and
readers are referred to \citet{knigge:1995} and \citet{long:2002} for
details.

@@

In order to calculate the dust scattering and absorption cross section
as a function of wavelength, the optical constants of
\citet{draine:1984} for amorphous carbon grains and
\citet{hanner:1988} for silicate grains are used. The model uses the
{}``large grain'' dust model of \citet{wood:2002} in which the dust
grain size distribution is described by the following function:
\begin{equation}
  n\left(a\right)da = \left(C_{\mathrm{C}}+C_{\mathrm{Si}}\right)\,
  a^{-p}\exp\left[-\left(\frac{a}{a_{c}}\right)^{q}\right]da
  \label{eq:grain-dist-function}
\end{equation}
where $a$ is the grain size restricted between $a_{\mathrm{min}}$ and
$a_{\mathrm{max}}$, and $C_{\mathrm{C}}$ and $C_{\mathrm{Si}}$ are the
terms set by requiring the grains to completely deplete a solar
abundance carbon and silicon. The parameters adopted in our model are:
$C_{\mathrm{C}}=1.32\times10^{-17}$,
$C_{\mathrm{Si}}=1.05\times10^{-17}$, $p=3.0$, $q=0.6$,
$a_{\mathrm{\mathrm{min}}}=0.1\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
$a_{\mathrm{\mathrm{max}}}=1000\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
and $a_{c}=50\,\mathrm{\mathrm{\mathrm{\mu m}}}$. This corresponds to
Model~1 of the dust model used by \citet{wood:2002}. See also their
Fig.~3 The relative numbers of each grain is assumed to be that of
solar abundance, C/H$\sim 3.5\times10^{-4}$ \citep{anders:1989} and
Si/H$\sim 3.6\times10^{-5}$ \citep{grevesse:1993} which are similar to
values found in the ISM model of \citet*{mathis:1977} and
\citet*{kim:1994}.

@@

The optical depth $\tau$ is equation~\ref{eq:formal_sol_integral}
is defined as: 
\[
\tau\left(t\right)\equiv\int_{t}^{\infty}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'
\]
where $\chi_{\nu}$ is the opacity of media the ray passes through.
$\tau_{\infty}$ is the total optical depth measured from the initial
ray point to the observer (or to the outer boundary closer to the
observer). Initially, the optical depth segments $\mathrm{d\tau}$
are computed at the intersections of a ray with the original AMR grid
in which the opacity and emissivity information are stored. For high
optical depth models, additional points are inserted between the original
points along the ray, and $\eta_{\nu}$ are $\chi_{\nu}$ values are
interpolated to those points to ensure $\mathrm{d}\tau<0.05$ for
the all ray segments.

@@

  \caption{The effect of line broadening on H$\alpha$. A model
    computed with a damping constant ($\Gamma$), described in
    section~\ref{sec:radiative-transfer-model} (solid), is compared with
    a model with no damping, $\Gamma=0$ (dashed).  Both models are
    computed with $T_{\mathrm{max}}=7500~\Kelvin$, $i=55^{\circ}$, and the
    reference parameters given in Table~\ref{tab:std_parameters}. The two
    models have similar peak flux levels (around $V \sim 0~\kmps$), but
    the total flux and the EW of the line increased drastically for the
    model with the damping constant. The broad wings extend to $\sim \pm
    800 \kmps$.  The redshifted absorption feature (very weakly) seen in
    the $\Gamma=0$ model is not seen in the model with the broadening.  }

@@

As in the disc-wind only models
(Fig.~\ref{fig:atlas_discwind_only}), the location of the absorption
component moves toward the line centre as the value of $\beta$
increases.  The figure shows that in the models with smaller $\beta$
and $T_{\mathrm{wind}}$, the line emission from the magnetosphere
dominates, while this situation reverses for the models with larger
$\beta$ and $T_{\mathrm{wind}}$. The model with
$\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
results in an H$\alpha$ profile that is far too strong to be
compatible with observations (\citealt{reipurth:1996} and
\citealt{alencar:2000}); however, the lower mass-loss rate models
(while keeping $\mu$ constant) produce profiles with the line
strengths comparable to observations.  Although the models in
Fig.~\ref{fig:atlas_hybrid} are computed with limited
ranges of $T_{\mathrm{wind}}$, $\beta$ and a fixed $i$, the resulting
profiles exhibit a wide variety of line profile shapes, many of which
are similar to the types of H$\alpha$ profiles seen in the observations
(c.f.~\citealt{reipurth:1996}).

@@

The effect of changing the ratio of the wind mass-loss rate to
mass-accretion rate
($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
in Fig.~\ref{fig:discwind_mu_effect}. With a fixed value of
mass-accretion rate
($\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$), the
mass-loss rate is varied. The figure shows that as $\mu$ increases the
P-Cygni absorption deepens only slightly., and the position of minimum flux in the
absorption trough appears to move blue-ward.  On the other hand, the
flux peak increase and the line wings become stronger as $\mu$
increases.  Although MHD models suggests (e.g.~\citealt{koenigl:2000})
that $\mu \sim 0.1$, the figure suggest that models a relatively wide range
of $\mu$  (e.g.~between 0.025 and 0.2 in this case)  reproduce the
profiles similar to observations.

@@

Although we have concentrated on CTTS here, the hybrid model is
equally applicable to pre-main-sequence stars across the mass
spectrum. Herbig Ae/Be star profiles are equally diverse, and whilst
many of the profiles are indicative of a wind
(\citet{finkenzeller:1984}) some lines may be explained by
magnetospheric accretion alone (e.g. \citealt{muzerolle:2005}). One
possible advantage in applying the hybrid model to the Herbig Ae/Be
systems is the growing observational data probing the line formation
region and inner disc using techniques such as spectro-astrometry
\citep[e.g.][]{baines:2006}, spectropolarimetry
\citep[e.g.][]{vink:2005} and interferometry
\citep[e.g.][]{monnier:2005}. These high-resolution techniques may aid
model fitting of individual objects by constraining some of the model
parameters, in particular the inclination.

@@

%
%----------------------------------------------------
% Bibliography follows here.
%-----------------------------------------------------
%
\bibliographystyle{mn}
\bibliography{mnras}

>>>>

\usepackage{babel}
\makeatother
\begin{document}
\title[On the formation of H$\alpha$ around classical T Tauri
  stars]{On the formation of H$\alpha$ line emission around classical
  T Tauri stars: the disc-wind-magnetosphere hybrid model}

@@

  \caption{Basic model configuration of the disc-wind-magnetosphere
    hybrid model. The system consist of four components: (1)~the
    continuum source located at the origin of the
    cartesian coordinates $\left(x,y,z\right)$ -- the $y$-axis is into
    the paper, (2)~the magnetospheric accretion flow, (3)~the disc
    wind, and (4)~the accretion disc. The disc wind originates from
    the disc surface between $w_{i}=R_{\mathrm{wi}}$ and
    $w_{i}=R_{\mathrm{wo}}$ where $w_{i}$ is the distance from the $z$
    axis on the equatorial plane.  The wind source
    points ($S$), from which the stream lines diverges, are placed at
    distance $d$ above and below the star. The degree of wind
    collimation is controlled by changing the value of $d$.}

@@

\citet*{knigge:1995} introduced the {}``split-monopole'' kinematic
disc-wind model in their studies of the UV resonance lines formed
in the winds of cataclysmic variable stars. Their formalism provides
a simple parameterisation of a disc wind that has similar properties 
to those found by  MHD modelling. In this model, the outflow
arises from the surface of the rotating accretion disc, and has a
biconical geometry. The specific angular momentum is assumed to be
conserved along a stream line, and the poloidal velocity component
is assumed to be simply a radial from vertically displaced {}``sources''
from the central star.  Here we briefly describe the disc-wind model, and
readers are referred to \citet{knigge:1995} and \citet{long:2002} for
details.

@@

In order to calculate the dust scattering and absorption cross section
as a function of wavelength, the optical constants of
\citet{draine:1984} for amorphous carbon grains and
\citet{hanner:1988} for silicate grains are used. The model uses the
{}``large grain'' dust model of \citet{wood:2002} in which the dust
grain size distribution is described by the following function:
\begin{equation}
  n\left(a\right)da = \left(C_{\mathrm{C}}+C_{\mathrm{Si}}\right)\,
  a^{-p}\exp\left[-\left(\frac{a}{a_{c}}\right)^{q}\right]da
  \label{eq:grain-dist-function}
\end{equation}
where $a$ is the grain size restricted between $a_{\mathrm{min}}$ and
$a_{\mathrm{max}}$, and $C_{\mathrm{C}}$ and $C_{\mathrm{Si}}$ are the
terms set by requiring the grains to completely deplete a solar
abundance carbon and silicon. The parameters adopted in our model are:
$C_{\mathrm{C}}=1.32\times10^{-17}$,
$C_{\mathrm{Si}}=1.05\times10^{-17}$, $p=3.0$, $q=0.6$,
$a_{\mathrm{\mathrm{min}}}=0.1\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
$a_{\mathrm{\mathrm{max}}}=1000\,\mathrm{\mathrm{\mathrm{\mu m}}}$,
and $a_{c}=50\,\mathrm{\mathrm{\mathrm{\mu m}}}$. This corresponds to
Model~1 of the dust model used by \citet{wood:2002}. See also their
Fig.~3.  The relative numbers of each grain is assumed to be that of
solar abundance, C/H$\sim 3.5\times10^{-4}$ \citep{anders:1989} and
Si/H$\sim 3.6\times10^{-5}$ \citep{grevesse:1993} which are similar to
values found in the ISM model of \citet*{mathis:1977} and
\citet*{kim:1994}.

@@

The optical depth $\tau$ is equation~\ref{eq:formal_sol_integral}
is defined as: 
\[
\tau\left(t\right)\equiv\int_{t}^{\tau_{\infty}}\chi_{\nu}\left(t'\right)\,\mathrm{d}t'
\]
where $\chi_{\nu}$ is the opacity of media the ray passes through.
$\tau_{\infty}$ is the total optical depth measured from the initial
ray point to the observer (or to the outer boundary closer to the
observer). Initially, the optical depth segments $\mathrm{d\tau}$
are computed at the intersections of a ray with the original AMR grid
in which the opacity and emissivity information are stored. For high
optical depth models, additional points are inserted between the original
points along the ray, and $\eta_{\nu}$ are $\chi_{\nu}$ values are
interpolated to those points to ensure $\mathrm{d}\tau<0.05$ for
the all ray segments.

@@

  \caption{The effect of line broadening on H$\alpha$. A model
    computed with a damping constant ($\Gamma$), described in
    section~\ref{sec:radiative-transfer-model} (solid), is compared with
    a model with no damping, $\Gamma=0$ (dashed).  Both models are
    computed with $T_{\mathrm{max}}=7500~\Kelvin$, $i=55^{\circ}$, and the
    reference parameters given in Table~\ref{tab:std_parameters}. The two
    models have similar peak flux levels (around $V \sim 0~\kmps$), but
    the total flux and the EW of the line increased drastically for the
    model with the damping constant. The broad wings extend to $\sim \pm
    800\,\kmps$.  The redshifted absorption feature (very weakly) seen in
    the $\Gamma=0$ model is not seen in the model with the broadening.  }

@@

As in the disc-wind only models
(Fig.~\ref{fig:atlas_discwind_only}), the location of the absorption
component moves toward the line centre as the value of $\beta$
increases.  The figure shows that in the models with smaller $\beta$
and $T_{\mathrm{wind}}$, the line emission from the magnetosphere
dominates, while this situation reverses for the models with larger
$\beta$ and $T_{\mathrm{wind}}$. The model with
$\left(T_{\mathrm{wind}},\,\beta\right)=\left(9000\,\mathrm{K},\,2.0\right)$
results in an H$\alpha$ profile that is far too strong to be
compatible with observations (\citealt{reipurth:1996} and
\citealt{alencar:2000}); however, the lower mass-loss rate models
(while keeping $\mu$ constant) produce profiles with the line
strengths comparable to observations (c.f.~appendix~\ref{sec:appendix}).
Although the models in Fig.~\ref{fig:atlas_hybrid} are computed with
limited ranges of $T_{\mathrm{wind}}$, $\beta$ and a fixed $i$, the
resulting profiles exhibit a wide variety of line profile shapes, many
of which are similar to the types of H$\alpha$ profiles seen in the
observations (c.f.~\citealt{reipurth:1996}).

@@

The effect of changing the ratio of the wind mass-loss rate to
mass-accretion rate
($\mu=\dot{M}_{\mathrm{wind}}/\dot{M}_{\mathrm{acc}}$) is demonstrated
in Fig.~\ref{fig:discwind_mu_effect}. With a fixed value of
mass-accretion rate
($\dot{M}_{\mathrm{acc}}=10^{-7}\,\mathrm{M_{\sun}\, yr^{-1}}$), the
mass-loss rate is varied. The figure shows that as $\mu$ increases the
P-Cygni absorption deepens only slightly, and the position of minimum
flux in the absorption trough appears to move blue-ward.  On the other
hand, the flux peak increase and the line wings become stronger as
$\mu$ increases.  Although MHD models suggests
(e.g.~\citealt{koenigl:2000}) that $\mu \sim 0.1$, the figure suggest
that models a relatively wide range of $\mu$ (e.g.~between 0.025 and
0.2 in this case) reproduce the profiles similar to observations.

@@

Although we have concentrated on CTTS here, the hybrid model is
equally applicable to pre-main-sequence stars across the mass
spectrum. Herbig Ae/Be star profiles are equally diverse, and whilst
many of the profiles are indicative of a wind
(\citealt{finkenzeller:1984}) some lines may be explained by
magnetospheric accretion alone (e.g. \citealt{muzerolle:2005}). One
possible advantage in applying the hybrid model to the Herbig Ae/Be
systems is the growing observational data probing the line formation
region and inner disc using techniques such as spectro-astrometry
\citep[e.g.][]{baines:2006}, spectropolarimetry
\citep[e.g.][]{vink:2005} and interferometry
\citep[e.g.][]{monnier:2005}. These high-resolution techniques may aid
model fitting of individual objects by constraining some of the model
parameters, in particular the inclination.

@@

%
%----------------------------------------------------
% Bibliography follows here.
%-----------------------------------------------------
%

%\bibliographystyle{mn}
%\bibliography{mnras}

\begin{thebibliography}{73}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Alencar} \& {Basri}(2000)}]{alencar:2000}
{Alencar} S.~H.~P., {Basri} G., 2000, \aj, 119, 1881

\bibitem[{{Alencar} {et~al.}(2005){Alencar}, {Basri}, {Hartmann}, \&
  {Calvet}}]{alencar:2005}
{Alencar} S.~H.~P., {Basri} G., {Hartmann} L., {Calvet} N., 2005, \aap, 440,
  595

\bibitem[{{Anders} \& {Grevesse}(1989)}]{anders:1989}
{Anders} E., {Grevesse} N., 1989, geochim. cosmochim. acta, 53, 197

\bibitem[{{Appenzeller} {et~al.}(2005){Appenzeller}, {Bertout}, \&
  {Stahl}}]{appenzeller:2005}
{Appenzeller} I., {Bertout} C., {Stahl} O., 2005, \aap, 434, 1005

\bibitem[{{Appenzeller} \& {Mundt}(1989)}]{appenzeller:1989}
{Appenzeller} I., {Mundt} R., 1989, \aapr, 1, 291

\bibitem[{{Baines} {et~al.}(2005){Baines}, {Oudmaijer}, {Porter}, \&
  {Pozzo}}]{baines:2006}
{Baines} D., {Oudmaijer} R., {Porter} J., {Pozzo} M., 2005, preprint
  (astro-ph/0512534)

\bibitem[{{Bertout} {et~al.}(1988){Bertout}, {Basri}, \&
  {Bouvier}}]{bertout:1988}
{Bertout} C., {Basri} G., {Bouvier} J., 1988, \apj, 330, 350

\bibitem[{{Blandford} \& {Payne}(1982)}]{blandford:1982}
{Blandford} R.~D., {Payne} D.~G., 1982, \mnras, 199, 883

\bibitem[{{Burrows} {et~al.}(1996){Burrows}, {Stapelfeldt}, {Watson}, {Krist},
  {Ballester}, {Clarke}, {Crisp}, {Gallagher}, {Griffiths}, {Hester},
  {Hoessel}, {Holtzman}, {Mould}, {Scowen}, {Trauger}, \&
  {Westphal}}]{burrows:1996}
{Burrows} C.~J. et al., 1996, \apj, 473, 437

\bibitem[{{Camenzind}(1990)}]{camenzind:1990}
{Camenzind} M., 1990, Reviews of Modern Astronomy, 3, 234

\bibitem[{{Castor} {et~al.}(1975){Castor}, {Abbott}, \& {Klein}}]{castor:1975}
{Castor} J.~I., {Abbott} D.~C., {Klein} R.~I., 1975, \apj, 195, 157

\bibitem[{{Castor} \& {Lamers}(1979)}]{castor:1979}
{Castor} J.~I., {Lamers} H.~J.~G.~L.~M., 1979, \apjs, 39, 481

\bibitem[{{Chiang} \& {Goldreich}(1997)}]{chiang:1997}
{Chiang} E.~I., {Goldreich} P., 1997, \apj, 490, 368

\bibitem[{{Collier Cameron} \& {Campbell}(1993)}]{cameron:1993}
{Collier Cameron} A., {Campbell} C.~G., 1993, \aap, 274, 309

\bibitem[{{Draine} \& {Lee}(1984)}]{draine:1984}
{Draine} B.~T., {Lee} H.~M., 1984, \apj, 285, 89

\bibitem[{{Drew} {et~al.}(1998){Drew}, {Proga}, \& {Stone}}]{drew:1998}
{Drew} J.~E., {Proga} D., {Stone} J.~M., 1998, \mnras, 296, L6

\bibitem[{{Edwards} {et~al.}(1987){Edwards}, {Cabrit}, {Strom}, {Heyer},
  {Strom}, \& {Anderson}}]{edwards:1987}
{Edwards} S., {Cabrit} S., {Strom} S.~E., {Heyer} I., {Strom} K.~M., {Anderson}
  E., 1987, \apj, 321, 473

\bibitem[{{Edwards} {et~al.}(1994){Edwards}, {Hartigan}, {Ghandour}, \&
  {Andrulis}}]{edwards:1994}
{Edwards} S., {Hartigan} P., {Ghandour} L., {Andrulis} C., 1994, \aj, 108, 1056

\bibitem[{{Finkenzeller} \& {Mundt}(1984)}]{finkenzeller:1984}
{Finkenzeller} U., {Mundt} R., 1984, \aaps, 55, 109

\bibitem[{{Frank} {et~al.}(2002){Frank}, {King}, \& {Raine}}]{frank:2002}
{Frank} J., {King} A., {Raine} D.~J., 2002, {Accretion Power in Astrophysics,
  3rd edn.} Cambridge Univ.\, Press, Cambridge, p. 398

\bibitem[{{Ghosh} {et~al.}(1977){Ghosh}, {Pethick}, \& {Lamb}}]{ghosh:1977}
{Ghosh} P., {Pethick} C.~J., {Lamb} F.~K., 1977, \apj, 217, 578

\bibitem[{Grevesse \& Noels(1993)}]{grevesse:1993}
Grevesse N., Noels A., 1993, in Origin and Evolution of the Elements, N.\ P.,
  E.\ V.-F., M.\ C., eds., Cambridge Univ.\, Press, Cambridge, p.~15

\bibitem[{{Gullbring} {et~al.}(1998){Gullbring}, {Hartmann}, {Briceno}, \&
  {Calvet}}]{gullbring:1998}
{Gullbring} E., {Hartmann} L., {Briceno} C., {Calvet} N., 1998, \apj, 492, 323

\bibitem[{{Hanner}(1988)}]{hanner:1988}
{Hanner} M., 1988, in NASA Conf. Pub. 3004, 22, Vol. 3004, p.~22

\bibitem[{{Harries}(2000)}]{harries:2000}
{Harries} T.~J., 2000, MNRAS, 315, 722

\bibitem[{{Hartigan} {et~al.}(1995){Hartigan}, {Edwards}, \&
  {Ghandour}}]{hartigan:1995}
{Hartigan} P., {Edwards} S., {Ghandour} L., 1995, \apj, 452, 736

\bibitem[{{Hartmann} {et~al.}(1982){Hartmann}, {Avrett}, \&
  {Edwards}}]{hartmann:1982}
{Hartmann} L., {Avrett} E., {Edwards} S., 1982, \apj, 261, 279

\bibitem[{{Hartmann} {et~al.}(1994){Hartmann}, {Hewett}, \&
  {Calvet}}]{hartmann:1994}
{Hartmann} L., {Hewett} R., {Calvet} N., 1994, \apj, 426, 669

\bibitem[{{Herbig}(1962)}]{herbig:1962}
{Herbig} G.~H., 1962, Advances in Astronomy and Astrophysics, 1, 47

\bibitem[{{Herbig} \& {Bell}(1988)}]{herbig:1988}
{Herbig} G.~H., {Bell} K.~R., 1988, {Catalog of emission line stars of the
  orion population}, Vol.~3. Lick Observatory Bulletin, Santa Cruz: Lick
  Observatory

\bibitem[{Hillier(1991)}]{hillier:1991}
Hillier D.~J., 1991, \aap, 247, 455

\bibitem[{{Johns-Krull} {et~al.}(1999){Johns-Krull}, {Valenti}, {Hatzes}, \&
  {Kanaan}}]{johns-krull:1999}
{Johns-Krull} C.~M., {Valenti} J.~A., {Hatzes} A.~P., {Kanaan} A., 1999, \apjl,
  510, L41

\bibitem[{{Kenyon} \& {Hartmann}(1987)}]{kenyon:1987}
{Kenyon} S.~J., {Hartmann} L., 1987, \apj, 323, 714

\bibitem[{{Kenyon} {et~al.}(1994){Kenyon}, {Hartmann}, {Hewett},
  {Carrasco}~{Cruz-Gonzalez}, {Recillas}, {Salas}, {Serrano}, {Strom}, {Strom},
  \& {Newton}}]{kenyon:1994}
{Kenyon} S.~J., {Hartmann} L., {Hewett} R., {Carrasco}~{Cruz-Gonzalez} I.,
  {Recillas} E., {Salas} L., {Serrano} A., {Strom} K.~M., {Strom} S.~E.,
  {Newton} G., 1994, \aj, 107, 2153

\bibitem[{{Kim} {et~al.}(1994){Kim}, {Martin}, \& {Hendry}}]{kim:1994}
{Kim} S., {Martin} P.~G., {Hendry} P.~D., 1994, \apj, 422, 164

\bibitem[{{Klein} \& {Castor}(1978)}]{klein:1978}
{Klein} R.~I., {Castor} J.~I., 1978, \apj, 220, 902

\bibitem[{{Knigge} {et~al.}(1995){Knigge}, {Woods}, \& {Drew}}]{knigge:1995}
{Knigge} C., {Woods} J.~A., {Drew} E., 1995, \mnras, 273, 225

\bibitem[{{K\"{o}nigl}(1991)}]{koenigl:1991}
{K\"{o}nigl} A., 1991, \apj, 370, L39

\bibitem[{{K\"{o}nigl} \& {Pudritz}(2000)}]{koenigl:2000}
{K\"{o}nigl} A., {Pudritz} R.~E., 2000, Protostars and Planets IV, 759

\bibitem[{{Krasnopolsky} {et~al.}(2003){Krasnopolsky}, {Li}, \&
  {Blandford}}]{krasnopolsky:2003}
{Krasnopolsky} R., {Li} Z.-Y., {Blandford} R.~D., 2003, \apj, 595, 631

\bibitem[{{Kuhi}(1964)}]{kuhi:1964}
{Kuhi} L.~V., 1964, \apj, 140, 1409

\bibitem[{{Kurosawa} {et~al.}(2004){Kurosawa}, {Harries}, {Bate}, \&
  {Symington}}]{kurosawa:2004a}
{Kurosawa} R., {Harries} T.~J., {Bate} M.~R., {Symington} N.~H., 2004, \mnras,
  351, 1134

\bibitem[{{Kurosawa} {et~al.}(2005){Kurosawa}, {Harries}, \&
  {Symington}}]{kurosawa:2005a}
{Kurosawa} R., {Harries} T.~J., {Symington} N.~H., 2005, \mnras, 358, 671

\bibitem[{{Kurucz}(1979)}]{kurucz:1979}
{Kurucz} R.~L., 1979, \apjs, 40, 1

\bibitem[{{Long} \& {Knigge}(2002)}]{long:2002}
{Long} K.~S., {Knigge} C., 2002, \apj, 579, 725

\bibitem[{{Luttermoser} \& {Johnson}(1992)}]{luttermoser:1992}
{Luttermoser} D.~G., {Johnson} H.~R., 1992, \apj, 388, 579

\bibitem[{{Martin}(1996)}]{martin:1996}
{Martin} S.~C., 1996, \apj, 470, 537

\bibitem[{{Mathis} {et~al.}(1977){Mathis}, {Rumpl}, \&
  {Nordsieck}}]{mathis:1977}
{Mathis} J.~S., {Rumpl} W., {Nordsieck} K.~H., 1977, \apj, 217, 425

\bibitem[{{Matt} \& {Pudritz}(2005)}]{matt:2005}
{Matt} S., {Pudritz} R.~E., 2005, \apjl, 632, L135

\bibitem[{{Mihalas}(1978)}]{mihalas:1978}
{Mihalas} D., 1978, {Stellar atmospheres, 2nd edn}. W.\ H.\ Freeman and Co.,
  San Francisco

\bibitem[{{Mohanty} {et~al.}(2005){Mohanty}, {Jayawardhana}, \&
  {Basri}}]{mohanty:2005}
{Mohanty} S., {Jayawardhana} R., {Basri} G., 2005, Memorie della Societa
  Astronomica Italiana, 76, 303

\bibitem[{{Monnier} {et~al.}(2005){Monnier}, {Millan-Gabet}, {Billmeier},
  {Akeson}, {Wallace}, {Berger}, {Calvet}, {D'Alessio}, {Danchi}, {Hartmann},
  {Hillenbrand}, {Kuchner}, {Rajagopal}, {Traub}, {Tuthill}, {Boden}, {Booth},
  {Colavita}, {Gathright}, {Hrynevych}, {Le Mignant}, {Ligon}, {Neyman},
  {Swain}, {Thompson}, {Vasisht}, {Wizinowich}, {Beichman}, {Beletic},
  {Creech-Eakman}, {Koresko}, {Sargent}, {Shao}, \& {van Belle}}]{monnier:2005}
{Monnier} J.~D. et al., 2005, \apj, 624, 832

\bibitem[{{Muzerolle} {et~al.}(2001){Muzerolle}, {Calvet}, \&
  {Hartmann}}]{muzerolle:2001}
{Muzerolle} J., {Calvet} N., {Hartmann} L., 2001, \apj, 550, 944

\bibitem[{{Muzerolle} {et~al.}(2005){Muzerolle}, {Luhman}, {Brice{\~n}o},
  {Hartmann}, \& {Calvet}}]{muzerolle:2005}
{Muzerolle} J., {Luhman} K.~L., {Brice{\~n}o} C., {Hartmann} L., {Calvet} N.,
  2005, \apj, 625, 906

\bibitem[{{Ouyed} \& {Pudritz}(1997)}]{ouyed:1997}
{Ouyed} R., {Pudritz} R.~E., 1997, \apj, 482, 712

\bibitem[{{Pudritz} \& {Banerjee}(2005)}]{pudritz:2005}
{Pudritz} R.~E., {Banerjee} R., 2005, in Cesaroni, R., Felli, M.,
Churchwell, E., Walmsley, M., eds, Proc.~IAU Symp. 225, Massive star
birth: A crossroads of Astrophysics, Cambridge University Press,
Cambridge,  p.~163

\bibitem[{{Ray} {et~al.}(1996){Ray}, {Mundt}, {Dyson}, {Falle}, \&
  {Raga}}]{ray:1996}
{Ray} T.~P., {Mundt} R., {Dyson} J.~E., {Falle} S.~A.~E.~G., {Raga} A.~C.,
  1996, \apjl, 468, L103

\bibitem[{{Reipurth} {et~al.}(1996){Reipurth}, {Pedrosa}, \&
  {Lago}}]{reipurth:1996}
{Reipurth} B., {Pedrosa} A., {Lago} M.~T.~V.~T., 1996, \aaps, 120, 229

\bibitem[{{Rybicki} \& {Hummer}(1978)}]{rybicki:1978}
{Rybicki} G.~B., {Hummer} D.~G., 1978, \apj, 219, 654

\bibitem[{{Shakura} \& {Sunyaev}(1973)}]{shakura:1973}
{Shakura} N.~I., {Sunyaev} R.~A., 1973, \aap, 24, 337

\bibitem[{{Shang} {et~al.}(2002){Shang}, {Glassgold}, {Shu}, \&
  {Lizano}}]{shang:2002}
{Shang} H., {Glassgold} A.~E., {Shu} F.~H., {Lizano} S., 2002, \apj, 564, 853

\bibitem[{{Shu} {et~al.}(1994){Shu}, {Najita}, {Ostriker}, {Wilkin}, {Ruden},
  \& {Lizano}}]{shu:1994}
{Shu} F.~H., {Najita} J., {Ostriker} E., {Wilkin} F., {Ruden} S., {Lizano} S.,
  1994, \apj, 429, 781

\bibitem[{{Symington} {et~al.}(2005{\natexlab{a}}){Symington}, {Harries}, \&
  {Kurosawa}}]{symington:2005}
{Symington} N.~H., {Harries} T.~J., {Kurosawa} R., 2005{\natexlab{a}}, \mnras,
  356, 1489

\bibitem[{{Symington} {et~al.}(2005{\natexlab{b}}){Symington}, {Harries},
  {Kurosawa}, \& {Naylor}}]{symington:2005b}
{Symington} N.~H., {Harries} T.~J., {Kurosawa} R., {Naylor} T.,
  2005{\natexlab{b}}, \mnras, 358, 977

\bibitem[{{Takami} {et~al.}(2003){Takami}, {Bailey}, \&
  {Chrysostomou}}]{takami:2003}
{Takami} M., {Bailey} J., {Chrysostomou} A., 2003, \aap, 397, 675

\bibitem[{{Uchida} \& {Shibata}(1985)}]{uchida:1985}
{Uchida} Y., {Shibata} K., 1985, \pasj, 37, 515

\bibitem[{{Ustyugova} {et~al.}(1995){Ustyugova}, {Koldoba}, {Romanova},
  {Chechetkin}, \& {Lovelace}}]{ustyugova:1995}
{Ustyugova} G.~V., {Koldoba} A.~V., {Romanova} M.~M., {Chechetkin} V.~M.,
  {Lovelace} R.~V.~E., 1995, \apjl, 439, L39

\bibitem[{{Vernazza} {et~al.}(1973){Vernazza}, {Avrett}, \&
  {Loeser}}]{vernazza:1973}
{Vernazza} J.~E., {Avrett} E.~H., {Loeser} R., 1973, \apj, 184, 605

\bibitem[{{Vink} {et~al.}(2005{\natexlab{a}}){Vink}, {Drew}, {Harries},
  {Oudmaijer}, \& {Unruh}}]{vink:2005}
{Vink} J.~S., {Drew} J.~E., {Harries} T.~J., {Oudmaijer} R.~D., {Unruh} Y.,
  2005{\natexlab{a}}, \mnras, 359, 1049

\bibitem[{{Vink} {et~al.}(2005{\natexlab{b}}){Vink}, {Harries}, \&
  {Drew}}]{vink:2005a}
{Vink} J.~S., {Harries} T.~J., {Drew} J.~E., 2005{\natexlab{b}}, \aap, 430, 213

\bibitem[{{White} \& {Basri}(2003)}]{white:2003}
{White} R.~J., {Basri} G., 2003, \apj, 582, 1109

\bibitem[{{Whitney} {et~al.}(2003){Whitney}, {Wood}, {Bjorkman}, \&
  {Wolff}}]{whitney:2003a}
{Whitney} B.~A., {Wood} K., {Bjorkman} J.~E., {Wolff} M.~J., 2003, \apj, 591,
  1049

\bibitem[{{Wood} {et~al.}(2002){Wood}, {Wolff}, {Bjorkman}, \&
  {Whitney}}]{wood:2002}
{Wood} K., {Wolff} M.~J., {Bjorkman} J.~E., {Whitney} B., 2002, \apj, 564, 887

\end{thebibliography}
